Precision calculations of cosmic shear projections

### 2017-02-12 authors.tex
minor update to affiliation and acknowledgements

\author[Heymans, Asgari, Joudaki et al.]
{C. Heymans$^1$\thanks{Email: heymans@roe.ac.uk}, 
M. Asgari$^1$, 
S. Joudaki$^2$, 
J. Harnois-D\'eraps$^1$,
H. Hildebrandt$^3$,
\newauthor
M. Kilbinger$^4$,
F. K\"ohlinger$^5$,
K. Kuijken$^5$,
P. Schneider$^3$,
P. Simon$^3$,
\newauthor
L. Van Waerbeke$^6$,
M. Viola$^5$
\\
$^1$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
$^2$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
$^3$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
$^4$Laboratoire AIM, CEA Saclay - CNRS - Paris 6, Irfu/SAp, F-91191 Gif-sur-Yvette, France\\
$^5$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
$^6$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
}

>>>>

\author[M.~Kilbinger et~al.]
{Martin Kilbinger$^{1,2}$\thanks{E-mail: martin.kilbinger@cea.fr},
Catherine Heymans$^3$,
Marika Asgari$^3$, 
Shahab Joudaki$^{4,5}$, 
\newauthor
Peter Schneider$^6$,
Patrick Simon$^6$,
Joachim Harnois-D\'eraps$^3$,
Hendrik Hildebrandt$^6$,
\newauthor
Fabian K\"ohlinger$^7$,
Konrad Kuijken$^7$,
Ludovic Van Waerbeke$^8$ and
Massimo Viola$^7$
\\
$^1$CEA/Irfu/SAp Saclay, Laboratoire AIM, 91191 Gif-sur-Yvette, France\\
$^2$Institut d'Astrophysique de Paris, UMR7095 CNRS, Universit\'e Pierre \& Marie Curie, 98 bis boulevard Arago, 75014 Paris, France \\
$^3$Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK\\
$^4$Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, PO Box 218, Hawthorn, VIC 3122, Australia\\
$^5$ARC Centre of Excellence for All-sky Astrophysics (CAASTRO)\\
$^6$Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany\\
$^7$Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands\\
$^8$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada\\
}
